Normalized Coherence

### 2020-03-15 Analysis/03_Normalized_Coherence.Rmd
confidene interval table

# Getting 95% between internal/external edges from GOCC, KEGG and REACTOME pathways

```{r}
# Getting biogrid msig slopes
msig_frame_biogrid_ci = get_msig_ci(sub_cats = subcats, database = biogrid)

# Getting string msig slopes
msig_frame_string_ci = get_msig_ci(sub_cats = subcats, database = string)

# Getting string filtered msig slopes
msig_frame_string_filt_ci = get_msig_ci(sub_cats = subcats, database = string_filt)

# Saving the files
saveRDS(msig_frame_biogrid_ci, "Biogrid_Msig_CI.rds")
saveRDS(msig_frame_string_ci, "String_Msig_CI.rds")
saveRDS(msig_frame_string_filt_ci, "String_Filt_Msig_CI.rds")
```

@@

>>>>

@@

# Merging together the confidence intervals

```{r}
#Renaming names before joining and manipulating

#BIOGRID
dis_slopes_biogrid_ci = dis_slopes_biogrid_ci %>% ungroup() %>% dplyr::select(-Count) %>% dplyr::rename(`Biogrid Lower` = Lower, `Biogrid Upper` = Upper)

#STRING
dis_slopes_string_ci = dis_slopes_string_ci %>% ungroup() %>% dplyr::select(-Count) %>% dplyr::rename(`String Lower` = Lower, `String Upper` = Upper)

#STRING Filtered
dis_slopes_string_filt_ci = dis_slopes_string_filt_ci %>% ungroup() %>% dplyr::select(-Count) %>% dplyr::rename(`String Filt Lower` = Lower, `String Filt Upper` = Upper)

#Biogrid and STRING
ci = full_join(dis_slopes_biogrid_ci, dis_slopes_string_ci, by = c("Disease", "Category"))

#Merging in STRING Filtered
ci = full_join(ci, dis_slopes_string_filt_ci, by = c("Disease", "Category"))

write.csv(ci, 'Confidence_Intervals.csv', quote = FALSE)
```
